Bird beak's elaboration and innovation

### 2023-05-12 Analysis/04-Figure_with_ellipse__alternative.Rmd
grey version

```{r}
pdf(file = "../Manuscript/Figures/figure_phylo_spiro.pdf", height = 11.693, width = 8.268)
## Plot splitting
x <- 82
super_orders <- rbind(
      #"Paleognathae" = "Tinamiformes",  
      matrix(c(rep(1+x,  1), rep(2+x,  1), rep(3+x,  1)), 1, 3),
      #"Galloanserae" = c("Galliformes", "Anseriformes"),
      matrix(c(rep(4+x,  2), rep(5+x,  2), rep(6+x,  2)), 2, 3),
      #"Mirandornithes" = c("Podicipediformes"),
      matrix(c(rep(7+x,  1), rep(8+x,  1), rep(9+x,  1)), 1, 3),
      #"Columbimorphae" = c("Columbiformes", "Pterocliformes"),
      matrix(c(rep(10+x, 2), rep(11+x, 2), rep(12+x, 2)), 2, 3),
      #"Otidimorphae" = c("Otidiformes", "Cuculiformes", "Musophagiformes"),
      matrix(c(rep(13+x, 3), rep(14+x, 3), rep(15+x, 3)), 3, 3),
      #"Gruiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      #"Aequornithes" = c("Procellariiformes", "Sphenisciformes", "Ciconiiformes", "Pelecaniformes", "Suliformes"),
      matrix(c(rep(16+x, 5), rep(17+x, 5), rep(18+x, 5)), 5, 3),
      #"Strisores" = c("Caprimulgiformes", "Apodiformes"),
      matrix(c(rep(19+x, 2), rep(20+x, 2), rep(21+x, 2)), 2, 3),
      #"Charadriiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      #"Telluraves" = c("Trogoniformes", "Bucerotiformes", "Coraciiformes", "Piciformes", "Strigiformes", "Accipitriformes", "Falconiformes", "Psittaciformes", "Passeriformes")
      matrix(c(rep(22+x, 9), rep(23+x, 9), rep(24+x, 9)), 9, 3))

@@

@@

load(file = "../Data/Processed/tip_colours_super_orders.rda")
for(i in 1:8) {
    ## Plot each pannel
    wrap.plot.ellipses(i, tip_colours_super_orders, superorder_shapespace, results$super_results_between, ei.col = c("orange", "blue"), phylo.plot = TRUE)
}
dev.off()

>>>>

```{r}
pdf(file = "../Manuscript/Figures/figure_phylo_spiro_grey.pdf", height = 11.693, width = 8.268)
## Plot splitting
x <- 82
super_orders <- rbind(
      #"Paleognathae" = "Tinamiformes",  
      matrix(c(rep(1+x,  1), rep(2+x,  1), rep(3+x,  1)), 1, 3),
      #"Galloanserae" = c("Galliformes", "Anseriformes"),
      matrix(c(rep(4+x,  1), rep(5+x,  1), rep(6+x,  1)), 1, 3),
      matrix(0, 1, 3),
      #"Mirandornithes" = c("Podicipediformes"),
      matrix(c(rep(7+x,  1), rep(8+x,  1), rep(9+x,  1)), 1, 3),
      #"Columbimorphae" = c("Columbiformes", "Pterocliformes"),
      matrix(c(rep(10+x, 1), rep(11+x, 1), rep(12+x, 1)), 1, 3),
      matrix(0, 1, 3),
      #"Otidimorphae" = c("Otidiformes", "Cuculiformes", "Musophagiformes"),
      matrix(0, 1, 3),
      matrix(c(rep(13+x, 1), rep(14+x, 1), rep(15+x, 1)), 1, 3),
      matrix(0, 1, 3),
      #"Gruiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      #"Aequornithes" = c("Procellariiformes", "Sphenisciformes", "Ciconiiformes", "Pelecaniformes", "Suliformes"),
      matrix(0, 2, 3),
      matrix(c(rep(16+x, 1), rep(17+x, 1), rep(18+x, 1)), 1, 3),
      matrix(0, 2, 3),
      #"Strisores" = c("Caprimulgiformes", "Apodiformes"),
      matrix(c(rep(19+x, 1), rep(20+x, 1), rep(21+x, 1)), 1, 3),
      matrix(0, 1, 3),
      #"Charadriiformes" (NOT A SUPER ORDER)
      matrix(0, 1, 3),
      matrix(0, 4, 3),
      #"Telluraves" = c("Trogoniformes", "Bucerotiformes", "Coraciiformes", "Piciformes", "Strigiformes", "Accipitriformes", "Falconiformes", "Psittaciformes", "Passeriformes")
      matrix(c(rep(22+x, 1), rep(23+x, 1), rep(24+x, 1)), 1, 3),
      matrix(0, 4, 3))

@@

## Plotting the tree and getting the tip orders
# tip_colours_orders <- plot.short.tree(tree, shapespace, "level2", tip.order = tip_order)
# save(tip_colours_orders, file = "../Data/Processed/tip_colours_orders.rda")

## Non coloured version
grey.palette <- function(n) {return(rep("grey", n))}
tip_colours_orders <- plot.short.tree(tree, shapespace, "level2", tip.order = tip_order, colour.palette = black.palette)
tip_colours_orders[1:length(tip_colours_orders)] <- "black"

@@

load(file = "../Data/Processed/tip_colours_super_orders.rda")

## Black version
tip_colours_super_orders[1:length(tip_colours_super_orders)] <- "black"
## Grey version
# tip_colours_super_orders <- rep("darkgrey", length(tip_colours_super_orders))

for(i in 1:8) {
    ## Plot each pannel
    wrap.plot.ellipses(i, tip_colours_super_orders, superorder_shapespace, results$super_results_between, ei.col = c("orange", "blue"), phylo.plot = TRUE)
}
dev.off()
